3D Environment Generation Using Conditional Adversarial Networks

### 2019-12-08 writing/paper/paper.tex
Add results table

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}

@@

	Both models are built on top of the PyTorch framework \cite{paszke2019pytorch} and are trained for 200 epochs.

@@

	The resulting heightmaps can be imported into popular 3d modeling software including Unity, Unreal, Blender, and World Machine. For the purposes of visualizing these results, and because of the limited support for Linux in all of the previously listed softwares, we visualize results using a demo application called Fractscape. Fractscape includes elevation based texture mapping which happens to work very well for visualizing our terrain elevation data. Unity, Unreal, Blender and World Machine have a different workflow for painting textures, so using the generality of fractscape works best for our visualizations.

@@

	Subjective results of networks show that pix2pix performs much better than cyclegan. For the specfic task of segmented image translation, paired training data allows the network to learn the meaning of the segmentations much better. Cyclegan had issues of keeping the semantic meaning in tact, even though it does appear to generate some of the patterns correctly, it's often mapped to the wrong brush or user defined section.

@@

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{floatpag}

@@

	Both models are built on top of the PyTorch framework \cite{paszke2019pytorch} and are trained for 200 epochs. We use the open source repo implemented by the Jun-Yan Zhu, who published the research on both models \cite{junyanzhu2017github}.

@@

	The resulting heightmaps can be imported into popular 3d modeling software including Unity, Unreal, Blender, and World Machine. For the purposes of visualizing these results, and because of the limited support for Linux in all of the previously listed softwares, we visualize results using a demo application called Fractscape. Fractscape includes elevation based texture mapping which happens to work very well for visualizing our terrain elevation data. Unity, Unreal, Blender and World Machine have a different workflow for painting textures, so using the generality of fractscape works best for our visualizations \cite{starscenesoftware2006}.

@@

	Subjective results of networks show that pix2pix performs much better than cyclegan. For the specfic task of segmented image translation, paired training data allows the network to learn the meaning of the segmentations much better. Cyclegan had issues of keeping the semantic meaning in tact. Even though it does appear to generate some of the patterns correctly, it's often mapped to the wrong brush or user defined section.

@@

	\begin{table*}[t]
	\thisfloatpagestyle{empty}
	\vspace{-2cm}
		\begin{tabular}{c|c|c|c|c}
 			Test Image & Original Pix2Pix & Augmented Pix2Pix & Original CycleGAN & Augmented CycleGAN \\
 			\hline
 				\includegraphics[trim=0 0 0 -20, width=0.25\columnwidth]{00.png} & \includegraphics[width=0.25\columnwidth]{01.png} & \includegraphics[width=0.25\columnwidth]{02.png} & \includegraphics[width=0.25\columnwidth]{03.png} & \includegraphics[width=0.25\columnwidth]{04.png} \\
 				\includegraphics[width=0.25\columnwidth]{10.png} & \includegraphics[width=0.25\columnwidth]{11.png} & \includegraphics[width=0.25\columnwidth]{12.png} & \includegraphics[width=0.25\columnwidth]{13.png} & \includegraphics[width=0.25\columnwidth]{14.png} \\
 				\includegraphics[width=0.25\columnwidth]{20.png} & \includegraphics[width=0.25\columnwidth]{21.png} & \includegraphics[width=0.25\columnwidth]{22.png} & \includegraphics[width=0.25\columnwidth]{23.png} & \includegraphics[width=0.25\columnwidth]{24.png} \\
 				\includegraphics[width=0.25\columnwidth]{30.png} & \includegraphics[width=0.25\columnwidth]{31.png} & \includegraphics[width=0.25\columnwidth]{32.png} & \includegraphics[width=0.25\columnwidth]{33.png} & \includegraphics[width=0.25\columnwidth]{34.png} \\
 				\includegraphics[width=0.25\columnwidth]{40.png} & \includegraphics[width=0.25\columnwidth]{41.png} & \includegraphics[width=0.25\columnwidth]{42.png} & \includegraphics[width=0.25\columnwidth]{43.png} & \includegraphics[width=0.25\columnwidth]{44.png} \\
 				\includegraphics[width=0.25\columnwidth]{50.png} & \includegraphics[width=0.25\columnwidth]{51.png} & \includegraphics[width=0.25\columnwidth]{52.png} & \includegraphics[width=0.25\columnwidth]{53.png} & \includegraphics[width=0.25\columnwidth]{54.png} \\
 				\includegraphics[width=0.25\columnwidth]{60.png} & \includegraphics[width=0.25\columnwidth]{61.png} & \includegraphics[width=0.25\columnwidth]{62.png} & \includegraphics[width=0.25\columnwidth]{63.png} & \includegraphics[width=0.25\columnwidth]{64.png} \\
 				\includegraphics[width=0.25\columnwidth]{70.png} & \includegraphics[width=0.25\columnwidth]{71.png} & \includegraphics[width=0.25\columnwidth]{72.png} & \includegraphics[width=0.25\columnwidth]{73.png} & \includegraphics[width=0.25\columnwidth]{74.png} \\
 				\includegraphics[width=0.25\columnwidth]{80.png} & \includegraphics[width=0.25\columnwidth]{81.png} & \includegraphics[width=0.25\columnwidth]{82.png} & \includegraphics[width=0.25\columnwidth]{83.png} & \includegraphics[width=0.25\columnwidth]{84.png} \\
 				\includegraphics[width=0.25\columnwidth]{90.png} & \includegraphics[width=0.25\columnwidth]{91.png} & \includegraphics[width=0.25\columnwidth]{92.png} & \includegraphics[width=0.25\columnwidth]{93.png} & \includegraphics[width=0.25\columnwidth]{94.png} \\

		\end{tabular}
	\end{table*}
